Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
reviewed introduction and related work

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{Bessa16}.  While this work
also makes use of a CEGIS-based technique, the approach is restricted to
synthesizing digital controllers for stable closed-loop systems described
via transfer function models.  In contrast, in the current paper we consider
a state-space representation of the physical system, which is known to present
various advantages over transfer function representation \cite{Astrom08}: (i) 
easy to generalize for the multivariate systems (i.e., with multiple inputs 
and outputs); (ii) shows the state-to-input relationships offering an internal 
model of the system; and (iii) allows to synthesize control systems that ensures
properties about the internal dynamics, e.g., to synthesize controllers that make
the closed-loop system \emph{safe}. This work focuses in the \emph{safety} of 
internal states, such property is usually overlooked in the previous cited 
works, but plays an important role in real world systems, where systems states 
cannot assume any real value. Moreover, this work integrates an
abstraction/refinement step inside the main CEGIS loop.

>>>>

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$s, i.e., most controllers can be synthesized in less
than $17.2$ seconds.

@@

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
also makes use of a CEGIS-based technique, the approach is restricted to
synthesizing digital controllers for stable closed-loop systems described
via transfer function models.  In contrast, in the current paper we consider
a state-space representation of the physical system, which is known to present
various advantages over transfer function representation \cite{Astrom08}: (i) 
easy to generalize for the multivariate systems (i.e., with multiple inputs 
and outputs); (ii) shows the state-to-input relationships offering an internal 
model of the system; and (iii) allows to synthesize control systems that ensures
properties about the internal dynamics, e.g., to synthesize controllers that make
the closed-loop system \emph{safe}. This work focuses in the \emph{safety} of 
internal states, such property is usually overlooked in the previous cited 
works, but plays an important role in real world systems, where systems states 
cannot assume any real value. Moreover, this work integrates an
abstraction/refinement step inside the main CEGIS loop.
